---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README/README-",
  cache.path = "man/cache/README/",
  out.width = "100%"
)
```

# SEMCOA - Composite Overfit Analysis for Structural Equation Models

`semcoa` is an R package to conduct the Composite Overfit Analysis (COA) framework for Structural Equation Models (SEM), and to then report and plot results.

## Installation

```{r eval=FALSE}
# install.packages("devtools")
devtools::install_github("sem-in-r/semcoa")
```

## Required Libraries

Please install following packages:

- seminr    (composite model estimation)
- rpart     (decision tree)
- maptools  (plotting labels)

## Testing

Until this project becomes a full-fledged R package, run all tests using:

```{r eval=FALSE}
source("tests/testthat.R")
```

Or run specific tests:

```{r eval=FALSE}
test_file("tests/testthat/test-integration-coa.R")
test_file("tests/testthat/test-unit-dtree.R")
```

## Demo

Look at [demos](demos/) folder for more examples

First, setup your composite construct-based model using the seminr package for specifying structural equation models.

```{r utaut-seminr, eval=TRUE, echo=FALSE, cache=TRUE}
library(seminr)

### UTAUT EXAMPLE

# Load the project data  ----
utaut_mm <- constructs(
  composite("PE", multi_items("PERF", 1:4)),
  composite("EE", c("PEOU1","PEOU3","PEOU5","PEOU6")),
  composite("SI", c(multi_items("NORM", 1:2),"INFL3")),
  composite("FC", multi_items("FACL", 1:4)),
  composite("HM", multi_items("MOTIV", 1:3)),
  composite("PV", multi_items("VALUE", 1:3)),
  composite("HAB", multi_items("HAB", 1:4)),
  composite("BI", multi_items("INT", 1:3)),
  composite("Exp", single_item("Experience")),
  composite("Age", single_item("age")),
  composite("Gender", single_item("gender"))
)

utaut_sm <- relationships(
  paths(from = c("PE", "EE", "SI", "FC", "HM", "PV", "HAB",
                 "Exp","Age","Gender"),
        to = "BI")
)

# Estimate model and run deviance trees
utaut_data <- read.csv(file = "data/trello_utaut.csv")[,-66]

utaut_model <- estimate_pls(data = utaut_data,
                            measurement_model = utaut_mm,
                            structural_model = utaut_sm)
```


Now we can conduct our overfit analysis:

```{r utaut-semcoa, eval=TRUE, cache=TRUE}
library(semcoa)
library(rpart)
library(maptools)

utaut_overfit <- coa(pls_model = utaut_model, 
                     focal_construct = "BI",
                     params = c("path_coef", "rSquared"))
```

You can visualize your predictive deviant cases and groups as follows:

```{r utaut-pd-plot, cache=TRUE, fig.height = 4, asp=0.66, fig.align = "left"}
plot_pd(utaut_overfit)
```

And you can inspect more details about the groups by inspecting their node IDs and seeing the defining descriptive characteristics of groups.

```{r utaut-coa-groups, echo=TRUE, cache=TRUE}
# Get all the names of the groups
names(utaut_overfit$dtree$deviant_groups)

# Get descriptive characteristics of one of the groups
group_rules("72", utaut_overfit$dtree)
```


And finally, you can examine unstable paths:

```{r utaut-coa-unstable, echo=TRUE, cache=TRUE}
# TODO
```
